Check Coverage

### 2019-10-08 analysis/merge_data.Rmd
Add the number of traits input to the FD output

  as.tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = study, plot = plot) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot, "_fd.tsv"))
}

>>>>

  as.tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
    cbind(years, .) %>%
    mutate(study_id = study, plot = plot, n_traits = ncol(trait_mat)) %>%
    write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot, "_fd.tsv"))
}
